---
title: "Assignment 3 - Tasks 3 & 4"
author: "Grace Kumaishi"
date: "10/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(here)
library(kableExtra)
library(lubridate)
```

## Section 1: Size comparisons 

### 1) Read in the data

```{r}
urchins <- read_csv(here("data", "urchins.csv")) %>% 
  clean_names()
```

### 2) Exploratory data visualization
Compare the distribution of sizes between purple and read urchins using a faceted histogram and a boxplot graph. 

**Histogram:**
```{r}
ggplot(data = urchins, aes(x = size)) +
  geom_histogram(bins = 15) +
  facet_wrap(~common_name)
```

**Boxplot: **
```{r}
ggplot(data = urchins, aes(x = common_name, y = size)) +
  geom_boxplot() 
```

### 3) Descriptive statistics table
Create a summary table that contains the following statistics for purple and red urchins: mean, median, standard deviation, and sample size. 

```{r}
urchin_stats <- urchins %>% 
  group_by(common_name) %>% 
  summarize(mean_size = mean(size),
            median_size = median(size),
            sd_size = sd(size),
            n = n())

kbl(urchin_stats) %>% 
  kable_styling()
```

### 4) Add a summary briefly describing overall takeaways about how size compares between the two species.
By looking at the graphs and table above, it appears that Red Urchins tend to grow to be larger than Purple Urchins. **ADD MORE HERE**


## Section 2: Purple urchin counts by site and year

### 1) Create a stored subset of the urchins data
-Filter to only include observations for purple urchins
-Convert the date to class "Date"
-Create a new column that only contains the year
-Create a new column called site_full that contains the full name for each site

```{r}
purple_urchins <- urchins %>% 
  filter(common_name == "Purple Urchin") %>% 
  mutate(date_new = mdy(date)) %>%
  mutate(year = year(date_new)) %>% 
  mutate(full_site_name = case_when( 
    site == "NAPL" ~ "Naples Reef", 
    site == "AQUE" ~ "Arroyo Quemado Reef",
    site == "CARP" ~ "Carpinteria Reef",
    site == "MOHK" ~ "Mohawk Reef",
    site == "IVEE" ~ "Isla Vista Reef"))
```

### 2) Make a summary table containing the total number of purple urchins observed by site and year

```{r}
purple_urchins_stats <- purple_urchins %>% 
  count(year, full_site_name) # ADD table using kableEXTRA?
```

### 3) Make an exploratory graph

```{r}
ggplot(data = purple_urchins_stats, aes(x = year, y = n)) +
  geom_line() +
  facet_wrap(~full_site_name)
```




