---
title: "Assignment 3 - Task 4"
author: "Grace Kumaishi"
date: "10/30/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(here)
library(kableExtra)
library(lubridate)
```

### Size comparisons between treatments for purple urchins on Naples Reef (January 2010)

```{r, echo = TRUE, message = FALSE, warning = FALSE}
urchins <- read_csv(here("data", "urchins.csv")) %>% 
  clean_names()
```

### 1) Data Wrangling
Include only Naples Reef observations for purple urchins observed in January 2010

```{r, echo = TRUE, message = FALSE, warning = FALSE}
napl_purple <- urchins %>% 
  filter(common_name == "Purple Urchin") %>% 
  mutate(date_new = mdy(date)) %>%
  mutate(year = year(date_new)) %>% 
  mutate(month = month(date_new)) %>% 
  mutate(full_site_name = case_when( 
    site == "NAPL" ~ "Naples Reef", 
    site == "AQUE" ~ "Arroyo Quemado Reef",
    site == "CARP" ~ "Carpinteria Reef",
    site == "MOHK" ~ "Mohawk Reef",
    site == "IVEE" ~ "Isla Vista Reef")) %>% 
  filter(site == "NAPL") %>% 
  filter(year == 2010) %>% 
  filter(month == 1)

class(year) <- "Date"
class(month) <- "Date"
```

### 2) Histogram and QQ-plots
Look at and consider histograms and QQ-plots for the size distribution for each of the treatments (control and annual) to assess normality

```{r, echo = TRUE, message = FALSE, warning = FALSE}
ggplot(data = napl_purple, aes(x = size)) +
  geom_histogram(bins = 15) +
  facet_wrap(~treatment)

ggplot(data = napl_purple, aes(sample = size)) +
  geom_qq() +
  facet_wrap(~treatment)
```

**MAIN TAKEAWAYS:**

### 3) Descriptive Statistcs
Create a statistcs table for both groups including at least mean, standard deviation, and sample size. 

```{r, echo = TRUE, message = FALSE, warning = FALSE}
napl_purple_stats <- napl_purple %>% 
  group_by(treatment) %>% 
  summarize(mean_size = mean(size),
            median_size = median(size),
            sd_size = sd(size),
            n = n())

kbl(napl_purple_stats) %>% 
  kable_styling()
```

### 4) Two-sample t-test

```{r, echo = TRUE, message = FALSE, warning = FALSE}
control_sample <- napl_purple %>% 
  filter(treatment == "CONTROL") %>% 
  pull(size)

annual_sample <- napl_purple %>% 
  filter(treatment == "ANNUAL") %>% 
  pull(size)

t.test(x = control_sample, annual_sample)
```

### 5) Summarize
**Write a comprehensive statement comparing the means that provides meaningful discussion about the means difference beyond (but also including) the p-value, possibly including the actual means and standard deviations for each group, and the actual difference of percent difference in means:**

**Write the meaning of the p-value that you found in the t-test above:**







